---
title: "OI perception data explore"
author: "Louise Shepperd"
date: "`r Sys.Date()`"
output:   
  html_document: default
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)
library(dplyr)
library(ggplot2)
library(knitr)
library(papaja)
library(htmlTable)
library(magrittr)
library(Gmisc)
library(patchwork)
library(corrplot)
library(forcats)
library(vtable)

theme_set(theme_apa())

# colour palettes for plots http://www.cookbook-r.com/Graphs/Colors_(ggplot2)/
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

### Introduction

This document offers an exploratory overview of QUANTITATIVE data from the debrief questionnaire for the two language groups.This will also be explored in relation to participant demographic information and performance on the audiovisual matching task.

The research questions are as follows:

***RQ 2: What influence of written input are learners aware of regarding word learning?***

*2.1: What was the perceived influence of written input on their learning in the study?*  

*2.2: What were participants' beliefs around the importance of written input when learning new words more broadly?*

This document will explore each of these questions in turn.

```{r readData, include=FALSE, message=FALSE, warning=FALSE}
OI_infl_df <- read.delim(here("Data", "OI_influence_ID.csv"), header = TRUE, sep = ',', encoding = 'UTF-8')

OI_infl_df2 <- read.delim(here("Data", "OI_influence_OI.csv"), header = TRUE, sep = ',', encoding = 'UTF-8')

OI_infl_df3 <- read.delim(here("Data", "OI_influence_OI_Contrast.csv"), header = TRUE, sep = ',', encoding = 'UTF-8')
```

```{r dataClean, include=FALSE, message=FALSE, warning=FALSE}
#str(OI_infl_df)

names(OI_infl_df)[1]<- "ID"

OI_infl_df$ID<-as.factor(OI_infl_df$ID)
OI_infl_df$see_OI<-as.factor(OI_infl_df$see_OI)
OI_infl_df$see_arabic<-as.factor(OI_infl_df$see_arabic)
OI_infl_df$see_english<-as.factor(OI_infl_df$see_english)
OI_infl_df$no_spell<-as.factor(OI_infl_df$no_spell)
OI_infl_df$spelling.preference<-as.factor(OI_infl_df$spelling.preference)
OI_infl_df$OI.importance<-as.factor(OI_infl_df$OI.importance)
OI_infl_df$vision.hearing<-as.factor(OI_infl_df$vision.hearing)
OI_infl_df$headphones<-as.factor(OI_infl_df$headphones)
OI_infl_df$gender<-as.factor(OI_infl_df$gender)
OI_infl_df$education<-as.factor(OI_infl_df$education)
OI_infl_df$nationality<-as.factor(OI_infl_df$nationality)
OI_infl_df$location<-as.factor(OI_infl_df$location)
OI_infl_df$L1<-as.factor(OI_infl_df$L1)
OI_infl_df$level<-as.factor(OI_infl_df$level)
OI_infl_df$same_day<-as.factor(OI_infl_df$same_day)
OI_infl_df$Participant.Device.Type<-as.factor(OI_infl_df$Participant.Device.Type)
OI_infl_df$correct<-as.factor(OI_infl_df$correct)

#rename and relevel

OI_infl_df$see_OI = factor(OI_infl_df$see_OI, levels = c("start", "middle", "end", "no_see"), ordered = TRUE)

OI_infl_df$education = factor(OI_infl_df$education, levels = c("primary", "secondary", "professional qualification", "bachelors", "masters", "doctorate"), ordered = TRUE)

OI_infl_df$level = factor(OI_infl_df$level, levels = c("none", "beginner", "intermediate", "advanced", "nearnative"), ordered = TRUE)
```

### RQ 2.1  Perception of OI influence in the study

#### First notice OI

First of all, it was of interest to know whether or not people noticed the written forms, as some people mentioned durng piloting that they didn't see the written words or noticed them midway through word learning.

```{r seeOI-plot, echo=FALSE, message=FALSE, warning=FALSE}
plot_seeOI <- ggplot(data = OI_infl_df) +
  geom_bar(mapping = aes(x=see_OI, fill = L1))+
  theme_minimal() +
  facet_grid(.~L1)+
  theme(legend.position = "none")+
  labs(x="When did you first notice the English or Arabic spelling?", y="Count", title="When participants first noticed OI by L1") +
  scale_x_discrete(breaks=c("start", "middle", "end", "no_see"), labels=c("start", "middle", "end", "didn't see"))

plot_seeOI
```

#### OI preference

The table and plots below offers a summary of the variables regarding learner perception of OI during the study.

```{r OI-pref-table, echo=FALSE, message=FALSE, warning=FALSE}

OI_pref_tb <- select(OI_infl_df, see_english, see_arabic, no_spell, spelling.preference, L1)

st(OI_pref_tb, group = "L1")

```

```{r OI-pref-plots, echo=FALSE, message=FALSE, warning=FALSE}

plot_spellingPref <- ggplot(data = OI_infl_df) +
  geom_bar(mapping = aes(x=spelling.preference, fill = L1))+
  theme_minimal() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90))+
  facet_grid(.~L1)+
  scale_y_continuous(name="no. participants", limits = c(0,115))+
  labs(x="Preference to learn all of words with…", y="Count", title="Overall spelling preference")+
  scale_x_discrete(breaks=c("#N/A", "in_arabic", "in_english", "no_OI"), labels=c("n/a", "Arabic OI", "English OI", "audio-only"))


plot_seeEnglish <- ggplot(data = OI_infl_df) +
  geom_bar(mapping = aes(x=see_english, fill = L1))+
  theme_minimal() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90))+
  facet_grid(.~L1)+
  scale_y_continuous(name="no. participants", limits = c(0,115))+
  labs(x="Seeing English spelling…", y="Count", title="Influence of English OI")+
  scale_x_discrete(breaks=c("difficult", "easier", "no_diff", "no_notice"), labels=c("difficult", "easier", "no difference", "didn't notice"))

plot_seeArabic <- ggplot(data = OI_infl_df) +
  geom_bar(mapping = aes(x=see_arabic, fill = L1))+
  theme_minimal() +
  theme(legend.position = "none",
        axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 90))+
  facet_grid(.~L1)+
  scale_y_continuous(name="no. participants", limits = c(0,115))+
  labs(x="Seeing Arabic spelling…", y="Count", title="Influence of Arabic OI")+
  scale_x_discrete(breaks=c("difficult", "easier", "no_diff", "no_notice"), labels=c("difficult", "easier", "no difference", "didn't notice"))

plot_noSpell <- ggplot(data = OI_infl_df) +
  geom_bar(mapping = aes(x=no_spell, fill = L1))+
  theme_minimal() +
  theme(legend.position = "none",
        axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 90))+
  facet_grid(.~L1)+
  scale_y_continuous(name="no. participants", limits = c(0,115))+
  labs(x="Audio only…", y="Count", title="Influence of no OI")+
  scale_x_discrete(breaks=c("difficult", "easier", "no_diff", "no_notice"), labels=c("difficult", "easier", "no difference", "didn't notice"))

plot_spellingPref

plot_seeEnglish + plot_seeArabic + plot_noSpell

```

In order to see how L1 Arabic preferences related to L2 English experience, they were plotted against proficiency test score.

```{r plot-OIpref-prof, echo=FALSE, message=FALSE, warning=FALSE}

OI_infl_df_ar <- filter(OI_infl_df, L1 == "Arabic")

plot_arPref1 <- ggplot(data = OI_infl_df_ar) +
  geom_jitter(mapping = aes(x=spelling.preference, y=prof_test_score, color = spelling.preference))+
  theme_minimal() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90))+
  scale_y_continuous(name="Proficiency score", limits = c(0,12))+
  labs(x="Preference to learn all of words with…", title="OI preference by proficiency") +
  scale_x_discrete(breaks=c("#N/A", "in_arabic", "in_english", "no_OI"), labels=c("n/a", "Arabic OI", "English OI", "audio-only"))+
  geom_boxplot(data = OI_infl_df_ar,
               aes(x=spelling.preference, y=prof_test_score),
               width=0.15,
               position = position_dodge(0.9))


plot_arPref2 <- ggplot(data = OI_infl_df_ar) +
  geom_jitter(mapping = aes(x=see_english, y=prof_test_score, color = see_english))+
  theme_minimal() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90))+
  scale_y_continuous(name="Proficiency score", limits = c(0,12))+
  labs(x="Seeing English spelling…", y="Count", title="Influence of English OI")+
  scale_x_discrete(breaks=c("difficult", "easier", "no_diff", "no_notice"), labels=c("difficult", "easier", "no difference", "didn't notice"))+
  geom_boxplot(data = OI_infl_df_ar,
               aes(x=see_english, y=prof_test_score),
               width=0.15,
               position = position_dodge(0.9))

plot_arPref3 <- ggplot(data = OI_infl_df_ar) +
  geom_jitter(mapping = aes(x=see_arabic, y=prof_test_score, color = see_arabic))+
  theme_minimal() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90))+
  scale_y_continuous(name="Proficiency score", limits = c(0,12))+
  labs(x="Seeing Arabic spelling…", y="Count", title="Influence of Arabic OI")+
  scale_x_discrete(breaks=c("difficult", "easier", "no_diff", "no_notice"), labels=c("difficult", "easier", "no difference", "didn't notice"))+
  geom_boxplot(data = OI_infl_df_ar,
               aes(x=see_arabic, y=prof_test_score),
               width=0.15,
               position = position_dodge(0.9))

plot_arPref4 <- ggplot(data = OI_infl_df_ar) +
  geom_jitter(mapping = aes(x=no_spell, y=prof_test_score, color = no_spell))+
  theme_minimal() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90))+
  scale_y_continuous(name="Proficiency score", limits = c(0,12))+
 labs(x="Audio only…", y="Count", title="Influence of no OI")+
  scale_x_discrete(breaks=c("difficult", "easier", "no_diff", "no_notice"), labels=c("difficult", "easier", "no difference", "didn't notice"))+
  geom_boxplot(data = OI_infl_df_ar,
               aes(x=no_spell, y=prof_test_score),
               width=0.15,
               position = position_dodge(0.9))

plot_arPref1
  
plot_arPref2 + plot_arPref3 + plot_arPref4

```



### RQ 2.2  Perception of OI importance in general

```{r OI-import-plot, echo=FALSE, message=FALSE, warning=FALSE}
plot_OI_import <- ggplot(data = OI_infl_df) +
  geom_bar(mapping = aes(x=OI.importance, fill = L1))+
  theme_minimal() +
  theme(legend.position = "none")+
  facet_grid(.~L1)+
  labs(x="Early exposure to OI is important when learning new words", y="Count", title="When learning new words,is it important to see the spelling the first time you hear it?")+
  scale_x_discrete(breaks=c("#N/A", "no", "yes"), labels=c("n/a", "no", "yes"))
  

plot_OI_import
```

