---
title: "OI perception data explore"
author: "Louise Shepperd"
date: "`r Sys.Date()`"
output:   
  html_document: default
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)
library(dplyr)
library(ggplot2)
library(knitr)
library(papaja)
library(htmlTable)
library(magrittr)
library(Gmisc)
library(patchwork)
library(corrplot)
library(forcats)
library(vtable)

theme_set(theme_apa())

# colour palettes for plots http://www.cookbook-r.com/Graphs/Colors_(ggplot2)/
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

### Introduction

This document offers an exploratory overview of QUANTITATIVE data from the debrief questionnaire for the two language groups.This will also be explored in relation to participant demographic information and performance on the audiovisual matching task.

The research questions are as follows:

***RQ 2: What influence of written input are learners aware of regarding word learning?***

*2.1: What was the perceived influence of written input on their learning in the study?*  

*2.2: What were participants' beliefs around the importance of written input when learning new words more broadly?*

This document will explore each of these questions in turn.

```{r readData, include=FALSE, message=FALSE, warning=FALSE}
OI_infl_df <- read.delim(here("Data", "OI_influence_ID.csv"), header = TRUE, sep = ',', encoding = 'UTF-8')

OI_infl_df2 <- read.delim(here("Data", "OI_influence_OI.csv"), header = TRUE, sep = ',', encoding = 'UTF-8')

OI_infl_df3 <- read.delim(here("Data", "OI_influence_OI_Contrast.csv"), header = TRUE, sep = ',', encoding = 'UTF-8')
```

```{r dataClean, include=FALSE, message=FALSE, warning=FALSE}
#str(OI_infl_df)

names(OI_infl_df)[1]<- "ID"

OI_infl_df$ID<-as.factor(OI_infl_df$ID)
OI_infl_df$see_OI<-as.factor(OI_infl_df$see_OI)
OI_infl_df$see_arabic<-as.factor(OI_infl_df$see_arabic)
OI_infl_df$see_english<-as.factor(OI_infl_df$see_english)
OI_infl_df$no_spell<-as.factor(OI_infl_df$no_spell)
OI_infl_df$spelling.preference<-as.factor(OI_infl_df$spelling.preference)
OI_infl_df$OI.importance<-as.factor(OI_infl_df$OI.importance)
OI_infl_df$vision.hearing<-as.factor(OI_infl_df$vision.hearing)
OI_infl_df$headphones<-as.factor(OI_infl_df$headphones)
OI_infl_df$gender<-as.factor(OI_infl_df$gender)
OI_infl_df$education<-as.factor(OI_infl_df$education)
OI_infl_df$nationality<-as.factor(OI_infl_df$nationality)
OI_infl_df$location<-as.factor(OI_infl_df$location)
OI_infl_df$L1<-as.factor(OI_infl_df$L1)
OI_infl_df$level<-as.factor(OI_infl_df$level)
OI_infl_df$same_day<-as.factor(OI_infl_df$same_day)
OI_infl_df$Participant.Device.Type<-as.factor(OI_infl_df$Participant.Device.Type)
OI_infl_df$correct<-as.factor(OI_infl_df$correct)

#rename and relevel

OI_infl_df$see_OI = factor(OI_infl_df$see_OI, levels = c("start", "middle", "end", "no_see"), ordered = TRUE)

OI_infl_df$education = factor(OI_infl_df$education, levels = c("primary", "secondary", "professional qualification", "bachelors", "masters", "doctorate"), ordered = TRUE)

OI_infl_df$level = factor(OI_infl_df$level, levels = c("none", "beginner", "intermediate", "advanced", "nearnative"), ordered = TRUE)
```

### RQ 2.1  Perception of OI influence in the study

#### First notice OI

First of all, it was of interest to know whether or not people noticed the written forms, as some people mentioned durng piloting that they didn't see the written words or noticed them midway through word learning.

```{r seeOI-plot, echo=FALSE, message=FALSE, warning=FALSE}
plot_seeOI <- ggplot(data = OI_infl_df) +
  geom_bar(mapping = aes(x=see_OI, fill = L1))+
  theme_minimal() +
  facet_grid(.~L1)+
  labs(x="When did you first notice the English or Arabic spelling?", y="Count", title="When participants first noticed OI by L1")

plot_seeOI
```

#### OI preference

The table and plots below offers a summary of the variables regarding learner perception of OI during the study.

```{r OI-pref-table, echo=FALSE, message=FALSE, warning=FALSE}

OI_pref_tb <- select(OI_infl_df, see_english, see_arabic, no_spell, spelling.preference, L1)

st(OI_pref_tb, group = "L1")

```

```{r OI-pref-plots, echo=FALSE, message=FALSE, warning=FALSE}

plot_spellingPref <- ggplot(data = OI_infl_df) +
  geom_bar(mapping = aes(x=spelling.preference, fill = L1))+
  theme_minimal() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90))+
  facet_grid(.~L1)+
  scale_y_continuous(name="no. participants", limits = c(0,115))+
  labs(x="Preference and see all of words…", y="Count", title="Overall spelling preference")


plot_seeEnglish <- ggplot(data = OI_infl_df) +
  geom_bar(mapping = aes(x=see_english, fill = L1))+
  theme_minimal() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90))+
  facet_grid(.~L1)+
  scale_y_continuous(name="no. participants", limits = c(0,115))+
  labs(x="Seeing the words written in English letters…", y="Count", title="Percieved influence of English OI")

plot_seeArabic <- ggplot(data = OI_infl_df) +
  geom_bar(mapping = aes(x=see_arabic, fill = L1))+
  theme_minimal() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90))+
  facet_grid(.~L1)+
  scale_y_continuous(name="no. participants", limits = c(0,115))+
  labs(x="Seeing the words written in Arabic letters…", y="Count", title="Percieved influence of Arabic OI")

plot_noSpell <- ggplot(data = OI_infl_df) +
  geom_bar(mapping = aes(x=no_spell, fill = L1))+
  theme_minimal() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90))+
  facet_grid(.~L1)+
  scale_y_continuous(name="no. participants", limits = c(0,115))+
  labs(x="Hearing the words without the spelling…", y="Count", title="Percieved influence of no OI")

plot_spellingPref+plot_seeEnglish + plot_seeArabic + plot_noSpell

```

In order to see how L1 Arabic preferences related to L2 English experience, they were plotted against proficiency test score.

```{r plot-OIpref-prof, echo=FALSE, message=FALSE, warning=FALSE}

OI_infl_df_ar <- filter(OI_infl_df, L1 == "Arabic")

plot_arPref1 <- ggplot(data = OI_infl_df_ar) +
  geom_jitter(mapping = aes(x=spelling.preference, y=prof_test_score, color = spelling.preference))+
  theme_minimal() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90))+
  scale_y_continuous(name="Proficiency score", limits = c(0,12))+
  labs(x="Preference to see the words...", title="OI preference by proficiency")


plot_arPref2 <- ggplot(data = OI_infl_df_ar) +
  geom_jitter(mapping = aes(x=see_english, y=prof_test_score, color = see_english))+
  theme_minimal() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90))+
  scale_y_continuous(name="Proficiency score", limits = c(0,12))+
  labs(x="Seeing the words in English...", title="English OI influence by proficiency")

plot_arPref3 <- ggplot(data = OI_infl_df_ar) +
  geom_jitter(mapping = aes(x=see_arabic, y=prof_test_score, color = see_arabic))+
  theme_minimal() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90))+
  scale_y_continuous(name="Proficiency score", limits = c(0,12))+
  labs(x="Seeing the words in Arabic...", title="Arabic OI influence by proficiency")

plot_arPref4 <- ggplot(data = OI_infl_df_ar) +
  geom_jitter(mapping = aes(x=no_spell, y=prof_test_score, color = no_spell))+
  theme_minimal() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90))+
  scale_y_continuous(name="Proficiency score", limits = c(0,12))+
  labs(x="Hearing the words without the spelling...", title="no OI influence by proficiency")

plot_arPref1 + plot_arPref2 + plot_arPref3 + plot_arPref4

```



### RQ 2.2  Perception of OI importance in general

```{r OI-import-plot, echo=FALSE, message=FALSE, warning=FALSE}
plot_OI_import <- ggplot(data = OI_infl_df) +
  geom_bar(mapping = aes(x=OI.importance, fill = L1))+
  theme_minimal() +
  facet_grid(.~L1)+
  labs(title="In general, when learning new words do you think it is important to see the spelling the first time you hear it?")

plot_OI_import
```

