---
title: "OI perception data QCA overview"
author: "Louise Shepperd"
date: "`r Sys.Date()`"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)
library(dplyr)
library(ggplot2)
library(knitr)
library(papaja)
library(htmlTable)
library(magrittr)
library(Gmisc)
library(patchwork)
library(corrplot)
library(forcats)
library(vtable)
library(Cairo)
library(ggwordcloud)
library(DiagrammeR)
library(treemap)

theme_set(theme_apa())

# colour palettes for plots http://www.cookbook-r.com/Graphs/Colors_(ggplot2)/
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

### Introduction

This document offers an exploratory overview of QUALITATIVE data from the debrief questionnaire for the two language groups.This will also be explored in relation to participant demographic information and performance on the audiovisual matching task.

The research questions are as follows:

***RQ 2: What influence of written input are learners aware of regarding word learning?***

*2.1: What was the perceived influence of written input on their learning in the study?*  

*2.2: What were participants' beliefs around the importance of written input when learning new words more broadly?*

This document will explore each of these questions in turn.

```{r readData, include=FALSE, message=FALSE, warning=FALSE}
OI_infl_QCA <- read.delim(here("Data", "OI_influence_QCA_codes.csv"), header = TRUE, sep = ',', encoding = 'UTF-8')
```

```{r dataClean, include=FALSE, message=FALSE, warning=FALSE}
#str(OI_infl_df)

names(OI_infl_QCA)[1]<- "ID"

OI_infl_QCA$ID<-as.factor(OI_infl_QCA$ID)
OI_infl_QCA$see_OI<-as.factor(OI_infl_QCA$see_OI)
OI_infl_QCA$see_arabic<-as.factor(OI_infl_QCA$see_arabic)
OI_infl_QCA$see_english<-as.factor(OI_infl_QCA$see_english)
OI_infl_QCA$no_spell<-as.factor(OI_infl_QCA$no_spell)
OI_infl_QCA$spelling.preference<-as.factor(OI_infl_QCA$spelling.preference)
OI_infl_QCA$resp_lang1<-as.factor(OI_infl_QCA$resp_lang1)
OI_infl_QCA$general_influence1<-as.factor(OI_infl_QCA$general_influence1)
OI_infl_QCA$category1<-as.factor(OI_infl_QCA$category1)
OI_infl_QCA$subcategory1<-as.factor(OI_infl_QCA$subcategory1)
OI_infl_QCA$OI.importance<-as.factor(OI_infl_QCA$OI.importance)
OI_infl_QCA$category2<-as.factor(OI_infl_QCA$category2)
OI_infl_QCA$subcategory2<-as.factor(OI_infl_QCA$subcategory2)
OI_infl_QCA$resp_lang2<-as.factor(OI_infl_QCA$resp_lang2)
OI_infl_QCA$vision.hearing<-as.factor(OI_infl_QCA$vision.hearing)
OI_infl_QCA$headphones<-as.factor(OI_infl_QCA$headphones)
OI_infl_QCA$gender<-as.factor(OI_infl_QCA$gender)
OI_infl_QCA$education<-as.factor(OI_infl_QCA$education)
OI_infl_QCA$nationality<-as.factor(OI_infl_QCA$nationality)
OI_infl_QCA$location<-as.factor(OI_infl_QCA$location)
OI_infl_QCA$L1<-as.factor(OI_infl_QCA$L1)
OI_infl_QCA$level<-as.factor(OI_infl_QCA$level)
OI_infl_QCA$same_day<-as.factor(OI_infl_QCA$same_day)
OI_infl_QCA$Participant.Device.Type<-as.factor(OI_infl_QCA$Participant.Device.Type)
OI_infl_QCA$correct<-as.factor(OI_infl_QCA$correct)

#rename and relevel

OI_infl_QCA$see_OI = factor(OI_infl_QCA$see_OI, levels = c("start", "middle", "end", "no_see"), ordered = TRUE)

OI_infl_QCA$education = factor(OI_infl_QCA$education, levels = c("primary", "secondary", "professional qualification", "bachelors", "masters", "doctorate"), ordered = TRUE)

OI_infl_QCA$level = factor(OI_infl_QCA$level, levels = c("none", "beginner", "intermediate", "advanced", "nearnative"), ordered = TRUE)
```

### RQ 2.1  Perception of OI influence in the study

#### Overall OI evaluation

create new dataset removing responses that couldn't be coded for general evaluation of whether OI was helpful or not. 

```{r remove-non-response1,message=FALSE, warning=FALSE}

OI_infl1 <- OI_infl_QCA %>% 
  filter(general_influence1 != "")
```

```{r OI-infl-table, echo=FALSE, message=FALSE, warning=FALSE}

OI_influence_tb <- select(OI_infl1,resp_lang1, general_influence1, category1,subcategory1, L1)

st(OI_influence_tb, group = "L1")
```

create another new dataset removing responses that couldn't be coded for specific type of OI influence. 

```{r remove-non-response2,message=FALSE, warning=FALSE}

OI_infl2 <- OI_infl1 %>% 
  filter(category1 != "")

OI_influence_tb2 <- select(OI_infl2,resp_lang1, general_influence1, category1,subcategory1, L1)

st(OI_influence_tb2, group = "L1")
```


```{r OI-infl-wordcloud, echo=FALSE, message=FALSE, warning=FALSE}

infl_codes <- OI_infl2 %>%
  group_by(L1, category1, general_influence1)%>%
  summarise(count=n())


infl_wordcloud <-  ggplot(infl_codes, aes(label = category1, color = general_influence1, size = count)) +
  geom_text_wordcloud_area() +
  facet_grid(~L1)+
  #scale_size_area(max_size = 40) +
  theme_minimal() + ggtitle("OI influence Word Cloud") 

infl_wordcloud

infl_plot<- ggplot(data = OI_infl2) +
  geom_bar(mapping = aes(x = L1, fill = category1), position = "fill")+
  facet_grid(~general_influence1)+
  theme_minimal()

infl_plot

infl_polar<- ggplot(data = OI_infl2) +
  geom_bar(mapping = aes(x = L1, fill = category1), show.legend = FALSE, width = 1)+
  #facet_grid(~general_influence1)+
  theme(aspect.ratio = 1)+
  labs(x = NULL, y = NULL)

infl_polar + coord_polar()
```

```{r OI-infl-plot, echo=FALSE, message=FALSE, warning=FALSE}

OI_influence <- ggplot(OI_infl_QCA, aes(x=L1, y=category1, colour=L1))+
  geom_count()+
  theme_minimal()+
  facet_grid(.~general_influence1)

OI_influence
```

```{r treemap1, echo=FALSE, message=FALSE, warning=FALSE}

infl_codes1 <- OI_infl2 %>%
  group_by(L1, general_influence1, category1, subcategory1)%>%
  summarise(count=n())


# treemap of all participants
treemap(infl_codes1,
            index=c("general_influence1","category1","subcategory1"),
            vSize="count",
            type="index",
        fontsize.labels=c(15,12,10),
        fontcolor.labels=c("white","white","white"),
        fontface.labels=c(2,1,3),
        #bg.labels=c("transparent"),
        align.labels=list(
        c("left", "top"),
        c("center", "center"), 
        c("right", "top")
        ),          
        overlap.labels=0.5,
        border.col=c("white","white", "white"),
        palette = cbPalette,
        title = "Treemap of percieved OI influence during word learning",
            )

# treemap of Arabic participants

infl_codesAR <- infl_codes1 %>% 
  filter(L1!= "English")

treemap(infl_codesAR,
            index=c("general_influence1","category1","subcategory1"),
            vSize="count",
            type="index",
        fontsize.labels=c(15,12,10),
        fontcolor.labels=c("white","white","white"),
        fontface.labels=c(2,1,3),
        #bg.labels=c("transparent"),
        align.labels=list(
        c("left", "top"),
        c("center", "center"), 
        c("right", "top")
        ),          
        overlap.labels=0.5,
        border.col=c("white","white", "white"),
        palette = cbPalette,
        title = "Treemap of L1 Arabic percieved OI influence during word learning",
            )

# treemap of Arabic participants

infl_codesEN <- infl_codes1 %>% 
  filter(L1!= "Arabic")

treemap(infl_codesEN,
            index=c("general_influence1","category1","subcategory1"),
            vSize="count",
            type="index",
        fontsize.labels=c(15,12,10),
        fontcolor.labels=c("white","white","white"),
        fontface.labels=c(2,1,3),
        #bg.labels=c("transparent"),
        align.labels=list(
        c("left", "top"),
        c("center", "center"), 
        c("right", "top")
        ),          
        overlap.labels=0.5,
        border.col=c("white","white", "white"),
        palette = cbPalette,
        title = "Treemap of L1 English percieved OI influence during word learning",
            )

```


#### Perceptions of OI influence

create new dataset removing responses that couldn't be coded for beliefs about OI importance. 

```{r remove-non-response3,message=FALSE, warning=FALSE}

OI_import1 <- OI_infl_QCA %>% 
  filter(category2 != "")
```

```{r OI-infl-table2, echo=FALSE, message=FALSE, warning=FALSE}

OI_importance_tb <- select(OI_import1,resp_lang2, OI.importance, category2,subcategory2, L1)

st(OI_importance_tb, group = "L1")
```

create another new dataset removing responses that related to the experiment and not learning in general. 

```{r remove-non-response4,message=FALSE, warning=FALSE}

OI_import2  <- OI_import1  %>% 
  filter(category2 != "(about the experiment)")

OI_importance_tb2 <- select(OI_import2,resp_lang2, OI.importance, category2,subcategory2, L1)

st(OI_importance_tb2, group = "L1")
```

Treemaps for RQ 2.2

```{r treemap2, echo=FALSE, message=FALSE, warning=FALSE}

infl_codes2 <- OI_import2 %>%
  group_by(OI.importance, category2,subcategory2, L1)%>%
  summarise(count=n())

# treemap of all participants
treemap(infl_codes2,
            index=c("OI.importance","category2","subcategory2"),
            vSize="count",
            type="index",
        fontsize.labels=c(15,12,10),
        fontcolor.labels=c("white","white","white"),
        fontface.labels=c(2,1,3),
        #bg.labels=c("transparent"),
        align.labels=list(
        c("center", "top"),
        c("center", "center"), 
        c("right", "bottom")
        ),          
        overlap.labels=0.5,
        border.col=c("white","white", "white"),
        palette = cbPalette,
        title = "Treemap of percieved OI importance during early word learning",
            )

# treemap of Arabic participants

infl_codes2AR <- infl_codes2 %>% 
  filter(L1!= "English")

treemap(infl_codes2AR,
            index=c("OI.importance","category2","subcategory2"),
            vSize="count",
            type="index",
        fontsize.labels=c(15,12,10),
        fontcolor.labels=c("white","white","white"),
        fontface.labels=c(2,1,3),
        #bg.labels=c("transparent"),
        align.labels=list(
        c("left", "top"),
        c("center", "center"), 
        c("right", "top")
        ),          
        overlap.labels=0.5,
        border.col=c("white","white", "white"),
        palette = cbPalette,
        title = "Treemap of L1 Arabic percieved OI importance during early word learning",
            )

# treemap of Arabic participants

infl_codes2EN <- infl_codes2 %>% 
  filter(L1!= "Arabic")

treemap(infl_codes2EN,
            index=c("OI.importance","category2","subcategory2"),
            vSize="count",
            type="index",
        fontsize.labels=c(15,12,10),
        fontcolor.labels=c("white","white","white"),
        fontface.labels=c(2,1,3),
        #bg.labels=c("transparent"),
        align.labels=list(
        c("left", "top"),
        c("center", "center"), 
        c("right", "top")
        ),          
        overlap.labels=0.5,
        border.col=c("white","white", "white"),
        palette = cbPalette,
        title = "Treemap of L1 English percieved OI importance during early word learning",
            )

```